Duration - Analysis for Non-Expressive performances

### 2020-05-06 material/analysis/stim_n/analysis/duration.Rmd
change file path
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

# Duration Variability
```{r cv, echo = FALSE}
# for each participant
cv <- dt_duration[EighthNote == "Yes", .(N = length(normDu), Mean = mean(normDu), SD = sd(normDu), CV = sd(normDu)/mean(normDu)), by = .(SubNr, TrialNr)]
print(cv)
```

>>>>

# Duration Variability
```{r cv, echo = FALSE}
# for each participant
cv <- dt_duration[EighthNote == "Yes", .(N = length(normDu), CV = sd(normDu)/mean(normDu)), by = .(SubNr, TrialNr)]
print(cv)
```
